\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-05 paper/paper.tex
Edits to paper (Eric, Thursday afternoon)

This paper presents a general framework for statistically modeling reliability field data from a heterogeneous population of components or subsystems operating within a larger population or fleet of systems. Such a model would be useful for applications such as making purchase decisions from among different suppliers of the components or subsystems.  Another application is making predictions for the number of needed replacement components or subsystems for spare part provisioning.

@@

The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work in the literature.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of the Backblaze data.  In Section~\ref{sec:Data}, we describe the Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard disk drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Finally, in Section~\ref{sec:Discussion}, we suggest potential applications of our model and consider limitation for inference implied by the model assumptions.

@@

\begin{equation} \Pr(T \le t) = F(t|\mu, \sigma) = 1 - \exp \left\{ -\exp \left[ \frac{ \log (t) - \mu }{\sigma} \right] \right\}\\
= \Phi_{SEV}\left[\frac{\log (t) - \mu}{\sigma}\right],
\end{equation}
where $\Phi_{SEV}$ is the cdf of the standard smallest extreme value distribution (SEV). Thus, the Weibull distribution is a log-location scale family, with $\log(T)$ following an SEV distribution with location parameter $\mu$ and scale parameter $\sigma$. With this in mind, the corresponding density function is
\begin{equation}
f(t|\mu, \sigma) =\frac{1}{\sigma t} \phi_{SEV}\left[\frac{\log(t) - \mu}{\sigma}\right]
\end{equation}

An advantage conferred by writing the model in this way is that the log of the $p$ quantile, $t_p$, is a linear function of the parameters, which allows an analyst to apply prior information in a straightforward way.  Using the inverse cdf of the SEV distribution, $\log(t_p) = \mu + \sigma \Phi_{SEV}^{-1}(p)$, this provides the following reparameterized version of the Weibull distribution
\begin{equation}
\Pr(T \le t) = F(t|\text{log}(t_p), \sigma) = \Phi_{SEV}\left[\frac{\log(\frac{t}{t_p}) + \sigma \Phi_{SEV}^{-1}(p)}{\sigma}\right]
\end{equation}
When there is more prior knowledge about a lower quantile, as is often the case with high-reliability products, using this parameterization allows the analyst to put prior distributions directly on those quantities. In addition, in the presence of censoring, $p$ can be chosen to make $\log(t_p)$ and $\sigma$ approximately independent. Since the choice of independent marginal priors is common in practice, this observation lends further credence to the use of these reparameterizations.

@@

As of the first quarter of 2016, Backblaze was collecting and reporting data on 63 different drive-models.  Some Drive-models have been running since 2013 or before, while others were added at a later date.  Data have been reported on 75,297 different hard drives that are or where in operation.  The number of drives varies by drive-model; some drive-models have only have a service record for a single drive whereas the maximum number of daily service records for a single drive model is 35,860.  Figure 1 shows a scatterplot of the total observed running time in hundred of thousands hours versus the total number of failures for drive-models with at least 3 failures.  For model identification, a minimum of three failures was the criterion for hard drive brands to be included in our analysis.

\begin{figure}[H]
  %\includegraphics[width=.9\textwidth]{data-sum.pdf}
  \includegraphics[width=.9\textwidth]{dm-summ-scatter.pdf}
  \caption{Scatterplot of total observed running time (hundred thousands of hours) versus total number of observed failures.  Each number labels a unique drive brand model.   Axes are on the log scale.}
  \label{drive-scatter}
\end{figure}

\subsection{Analysis of a Single Drive-Model}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, Drive-model 14.  The Kaplan-Meier estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures till about 10,000 hours (early failures), increases more rapidly from about 10,000 to 20,000 hours (presumably wearout failures).  In addition, computer hard drives are known to have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and a theoretical justification to apply the GLFP model.

@@

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions.  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Lognormal} \langle 1.7,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Lognormal}\langle 8.6, 5.6\times 10^7 \rangle$$
$$\mbox{logit}^{-1}\pi \sim \op{Logitnormal}\langle 1.0\times 10^{-3}, 7.1\times 10^{-1} \rangle,\quad
\sigma_1, \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with simultaneous confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier non-parametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to\cite[Chapter 11]{meeker} (see Appendix for a detailed description).

@@

Next, we model these parameters themselves as random variables, varying across the different sub-populations.  Let
\begin{equation*}
\sigma_{1g} \ind \op{Lognormal} \left( \eta_{\sigma_1}, \tau^2_{\sigma_1} \right)
\end{equation*}
\begin{equation*}
\sigma_{2g} \ind \op{Lognormal} \left( \eta_{\sigma_2}, \tau^2_{\sigma_2}\right)\op{T}\left(0, 1\right)
\end{equation*}
\begin{equation}
\label{eq:hier-model}
t_{p_{1}g} \equiv \mu_{1g} + \sigma_{1g}\,\Phi^{-1}(p_1)  \ind \op{Lognormal} \left(\eta_{t_{p_1}}, \tau^2_{t_{p_1}}\right)
\end{equation}
\begin{equation*}
t_{p_{2}g} \equiv \mu_{2g} + \sigma_{2g}\,\Phi^{-1}(p_2)  \ind \op{Lognormal} \left(\eta_{t_{p_2}}, \tau^2_{t_{p_2}}\right)
\end{equation*}
\begin{equation*}
\op{logit} \pi_g \ind \op{N}(\eta_\pi, \tau_\pi).
\end{equation*}

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of log quantile and scale since the data we encounter are more informative about the left side of their respective lifetime distribution. We truncate the distribution of $\sigma_{2g}$ at $1$, restricting the wearout failure mode to have an increasing hazard function (e.g., $0<\sigma_{2g}<1$). We choose to model these parameters with lognormal and normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan} \citep{rstan} package in {\tt R} \citep{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\citep{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1, 2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factor was used to provide a check for adequate mixing of the multiple chains. Upon convergence, $\hat{R}$, converges to 1.  The  maximum values of $\hat{R}$ across all model parameters for Models 1 throught 4 (5, 50, 95 and 140 parameters, respectively) were 1.005, 1.028, 1.009 and 1.004. Other diagnostics provided by the software (tree-depth, and divergent transitions) were clean. Plots of the posterior draws were inspected for parameters with the fewest effective samples; these did not suggest features that were inadequately explored.

@@

\subsection{Model Selection}
\label{sec:Model Comparisons}
As we have discussed, while we prefer to allow all of the GLFP model parameters to be drive-model specific, there are practical issues with fitting the full model. For example, due to heavy left-truncation, there may be insufficient information for particular drive-models to estimate all of the parameters.

@@

We can also compare the four Model fits for each drive-model individually.  For these comparisons, we use the posterior median of the MCMC draws. %Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

The GLFP fit for a representative selection of drive-models (Drive-models 2, 9, 14, and 40) are presented in Figure \ref{fig:mod_comp_leg} (See the Supplementary Material for similar plots for the other drive-models).  The black step functions again correspond to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to describe the observed failure data.  All of the GLFP models appear to produce lower estimates, relative to Kaplan-Meier, of the proportion of failed hard drives for Drive-model 2, with Model 4 being in closest agreement.  For Drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for Drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the nonparametric estimate quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for Drive-model 40.

@@

\begin{equation}
\mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] = \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{equation}

\noident Using this criterion, we should choose the Model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\frac{\sum_{i=1}^S w_{i,s} p(t_{g,i})}{\sum_{s=1}^S w_{i,s}}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  
Results showing estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
 We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.

@@

\subsection{Results}
\subsubsection{Model Assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the former.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the Kaplan-Meier estimate for each drive-model $g$.

@@

To attempt to diagnose the cause of the discrepancies between the observed data for Drive-model 4 and its posterior predictive distribution, we consider the event plot for a random sample of units for this Drive-model while looking at estimates of lifetime (Figure \ref{fig:ex-mod-4}). From these plots, we can see that the discrepancy between the posterior and the nonparametric estimate is driven by failure among a relatively small subset of units, namely those with left-truncation times smaller than 2500 hours. Further investigation reveals that, if we exclude the newest 75 drives, those with truncation times less than 800 hours, the nonparametric estimate falls within the posterior 90\% pointwise credible band. This situation suggests that, despite belonging to the same Drive-model, there may be something different about the newer drives leading to worse reliability.

@@

A similar pair of plots for Drive-model 43 illustrate (Figure \ref{fig:ex-mod-43}). The data for this Drive-model are heavily truncated; the observed units had run for quite some time before data were made available with the earliest left-truncation time at 12,189 hours. In Figure \ref{fig:ex-mod-43} we see that the lack of data for this Drive-model during early life results in a diffuse posterior centered around the what we call the ``global mean." The global mean is corresponds to $\op{GFLP}$ parameters taking the value of the hierarchical means, i.e., $\pi=\eta_{\pi}, \, \mu_2=\eta_{t_2} - \eta_{\sigma_2}\Phi^{-1}(.2)$ and $\sigma_2= \eta_{\sigma_2})$. This continues until about 10,000 hours at which time the posterior diverges from the global model, arriving at a compromise between it and the nonparametric estimate.

>>>>

This paper presents a general framework for statistically modeling reliability field data from a heterogeneous population of components or subsystems operating within a larger population or fleet of systems. Such a model would be useful for applications such as

\begin{itemize}
\item Making purchase decisions from among different suppliers of the components or subsystems
\item Making predictions for the number of needed replacement components or subsystems for spare part provisioning
\end{itemize}

@@

The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work in the literature.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of the Backblaze data.  In Section~\ref{sec:Data}, we describe the Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard disk drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. In Section~\ref{sec:Discussion}, we suggest potential applications of our model and consider limitation for inference implied by the model assumptions.

@@

\begin{equation} \Pr(T \le t) = F(t|\mu, \sigma) = 1 - \exp \left\{ -\exp \left[ \frac{ \log (t) - \mu }{\sigma} \right] \right\}\\
= \Phi_{SEV}\left[\frac{\log (t) - \mu}{\sigma}\right],
\end{equation}
where $\Phi_{SEV}$ is the cdf of the standard smallest extreme value distribution (SEV). Thus, the Weibull distribution is a log-location scale family, with $\log(T)$ following an SEV distribution with location parameter $\mu$ and scale parameter $\sigma$. 
% With this in mind, the corresponding density function is
% \begin{equation}
% f(t|\mu, \sigma) =\frac{1}{\sigma t} \phi_{SEV}\left[\frac{\log(t) - \mu}{\sigma}\right]
% \end{equation}

An advantage conferred by writing the model in this way is that the log of the $p$ quantile, $t_p$, is a linear function of the parameters, namely, $\log(t_p) = \mu + \sigma \Phi_{SEV}^{-1}(p)$. This allows an analyst to apply prior information in a straightforward way. Reparameterizing in terms of $(\log(t_p),\sigma)$, we can write the Weibull cdf as
\begin{equation}
\Pr(T \le t) = F(t|\text{log}(t_p), \sigma) = \Phi_{SEV}\left[\frac{\log(\frac{t}{t_p}) + \sigma \Phi_{SEV}^{-1}(p)}{\sigma}\right]
\end{equation}
When there is more prior knowledge about a lower quantile, as is often the case with high-reliability products, using this parameterization allows the analyst to put prior distributions directly on those quantities. In addition, in the presence of censoring, $p$ can be chosen to make $\log(t_p)$ and $\sigma$ approximately independent. Since the choice of independent marginal priors is common in practice, this observation lends further credence to the use of these reparameterizations.

@@

As of the first quarter of 2016, Backblaze was collecting and reporting data on 63 different drive-models.  Some drive-models have been running since 2013 or before, while others were added at a later date.  Data have been reported on 75,297 different hard drives that are or where in operation.  The number of drives varies by drive-model; some drive-models have only have a service record for a single drive whereas the maximum number of daily service records for a single drive-model is 35,860.  Figure 1 shows a scatterplot of the total observed running time in hundred of thousands hours versus the total number of failures for drive-models with at least 3 failures.  For model identification, a minimum of three failures was the criterion for hard drive brands to be included in our analysis.

\begin{figure}[H]
  %\includegraphics[width=.9\textwidth]{data-sum.pdf}
  \includegraphics[width=.9\textwidth]{dm-summ-scatter.pdf}
  \caption{Scatterplot of total observed running time (hundred thousands of hours) versus total number of observed failures.  Each number labels a unique drive-model.   Axes are on the log scale.}
  \label{drive-scatter}
\end{figure}

\subsection{Analysis of a single drive-model}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, Drive-model 14.  The Kaplan-Meier estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures till about 10,000 hours (early failures), increases more rapidly from about 10,000 to 20,000 hours (presumably wearout failures).  In addition, computer hard drives are known to have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and a theoretical justification to apply the GLFP model.

@@

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions.  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Lognormal} \langle 1.7,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Lognormal}\langle 8.6, 5.6\times 10^7 \rangle$$
$$\mbox{logit}^{-1}\pi \sim \op{Logitnormal}\langle 1.0\times 10^{-3}, 7.1\times 10^{-1} \rangle,\quad
\sigma_1, \sigma_2 \stackrel{ind.}{\sim} \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with simultaneous confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier non-parametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to\citet[Chapter 11, ]{meeker} (see Appendix for a detailed description).

@@

Next, we model these parameters themselves as random variables, varying across the different sub-populations.  Let
\begin{equation*}
\sigma_{1g} \ind \op{Log-normal} \left( \eta_{\sigma_1}, \tau^2_{\sigma_1} \right)
\end{equation*}
\begin{equation*}
\sigma_{2g} \ind \op{Log-normal} \left( \eta_{\sigma_2}, \tau^2_{\sigma_2}\right)\op{T}\left(0, 1\right)
\end{equation*}
\begin{equation}
\label{eq:hier-model}
t_{p_{1}g} \equiv \mu_{1g} + \sigma_{1g}\,\Phi^{-1}(p_1)  \ind \op{Log-normal} \left(\eta_{t_{p_1}}, \tau^2_{t_{p_1}}\right)
\end{equation}
\begin{equation*}
t_{p_{2}g} \equiv \mu_{2g} + \sigma_{2g}\,\Phi^{-1}(p_2)  \ind \op{Log-normal} \left(\eta_{t_{p_2}}, \tau^2_{t_{p_2}}\right)
\end{equation*}
\begin{equation*}
\pi_g \ind \op{Logit-normal}(\eta_\pi, \tau^2_\pi).
\end{equation*}

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of log quantile and scale since the data we encounter are more informative about the left side of their respective lifetime distribution. We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by``$T(0,1)$" above) restricting the wearout failure mode to have an increasing hazard function (e.g., $\beta_{2g} = 1/\sigma_{2g}>1$). We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan} \citep{rstan} package in {\tt R} \citep{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\citep{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1, 2 and 3 for a total of 6,000 post burn-in iterations and 16 chains were run for Model 4 for a total of 24,000 post burn-in iterations. The Gelman-Rubin potential scale reduction factor was used to provide a check for adequate mixing of the multiple chains. Upon convergence, $\hat{R}$, converges to 1.  The  respective maximum values of $\hat{R}$ across all model parameters for Models 1 through 4 (5, 50, 95 and 140 parameters, respectively) were 1.005, 1.028, 1.009 and 1.004. Other diagnostics provided by the software (tree-depth, and divergent transitions) did not indicate problems with sampling. Plots of the posterior draws were inspected for parameters with the fewest effective samples; these did not suggest features that were inadequately explored.

@@

\subsection{Model selection}
\label{sec:Model Comparisons}
As we have discussed, while we prefer to allow all of the GLFP model parameters to be drive-model specific, there are practical issues with fitting the full model. For example, due to heavy left-truncation, there may be insufficient information for particular drive-models to estimate all of the parameters.

@@

We can also compare posterior estimates of time to failure under Models 1-4 for each drive-model individually.  For these comparisons, we calculate, pointwise, the posterior median of proportion failing over a grid. That is, for every model, and for a fixed set, $\tilde{t}=\{\tilde{t}_1,\ldots,\tilde{t}_M\}$, we compute 
\begin{equation}
\op{median}\left\{\op{GLFP}\left(\tilde{t}_m|\pi_{g}^{(s)},\mu_{1g}^{(s)},\sigma_{1g}^{(s)},\mu_{2g}^{(s)},\sigma_{2g}^{(s)}\right);s=1,\ldots,S \right\},
\end{equation}
where $\theta^{(s)}$ is the $s^{th}$ posterior sample from $p(\theta|y)$.
%Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

The GLFP fit for a representative selection of drive-models (Drive-models 2, 9, 14, and 40) are presented in Figure \ref{fig:mod_comp_leg} (See the Supplementary Material for similar plots for the other drive-models).  The black step functions again correspond to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to describe the observed failure data.  All of the GLFP models appear to produce higher estimates of the proportion failing, relative to Kaplan-Meier, for Drive-model 2. This behavior is not unexpected, however, since hierarchical models improve model stability through shrinkage; in this context, shrinkage toward an average cumulative time to failure. Model 4 is in closest agreement.

Drive-model 9 shows a high proportion of  of early failures relative to Model 1. Model 2 addresses this by estimating an earlier time to wearout, but still results in a poor fit to the data. Models 3 and 4 conform more closely to the Kaplan-Meier. The disagreement between Models 3 and 4 for Drive-model 9, is interesting: Model 4 allows the proportion of defective units to vary by Drive-model, but Model 3 appears to fit just as well in this case, by increasing the scale parameter for the wearout failure mode.

For Drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for Drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the nonparametric estimate quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for Drive-model 40.

@@

\begin{equation}
\mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] = \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{equation}
\noindent Using this criterion, we should choose the Model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\frac{\sum_{i=1}^S w_{i,s} p(t_{g,i})}{\sum_{s=1}^S w_{i,s}}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  
Results showing estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
 We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.

@@

\subsection{Results}
\subsubsection{Model Assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the first of these.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the Kaplan-Meier estimate for each drive-model $g$.

@@

To diagnose the cause of the discrepancies between the observed data for Drive-model 4 and its posterior predictive distribution, we consider the event plot for a random sample of units for this Drive-model while looking at estimates of lifetime (Figure \ref{fig:ex-mod-4}). From these plots, we can see that the discrepancy between the posterior and the nonparametric estimate is driven by failure among a relatively small subset of units, namely those with left-truncation times smaller than 2500 hours. Further investigation reveals that, if we exclude the newest 75 drives, those with truncation times less than 800 hours, the nonparametric estimate falls within the posterior 90\% pointwise credible band. This situation suggests that, despite belonging to the same Drive-model, there may be something different about the newer drives leading to worse reliability.

@@

Figure 8 shows a similar pair of plots for Drive-model 43 illustrate (Figure \ref{fig:ex-mod-43}). The data for this Drive-model are heavily truncated; the observed units had run for quite some time before data were made available with the earliest left-truncation time at 12,189 hours. In Figure \ref{fig:ex-mod-43} we see that the lack of data for this Drive-model during early life results in a diffuse posterior centered around the what we call the ``global mean." The global mean is corresponds to $\op{GFLP}$ parameters taking the value of the hierarchical means, i.e., $\pi=\eta_{\pi}, \, \mu_2=\eta_{t_2} - \eta_{\sigma_2}\Phi^{-1}(.2)$ and $\sigma_2= \eta_{\sigma_2})$. This continues until about 10,000 hours at which time the posterior diverges from the global model, arriving at a compromise between it and the nonparametric estimate.
